Glue-on AdS holography for $T\bar T$-deformed CFTs

### 2023-06-22 alpha/GlueonAdS/glueon-slides.tex
Experiment with beamer alternatives
Add bare minimal version of slides

\documentclass[
	10pt
%	,draft
%	,handout
	,noamsthm
]{beamer}

\input{preamble.tex}

\usepackage{tikz}
%\usepackage{snapshot}

\title{Glue-on AdS holography for $T\bar T$-deformed CFTs}
\subtitle{An extended AdS\,/\,\TTbar duality \textit{(beyond infinity)}}
\author{%
	Wen-Xin Lai 
	\texstringonly{\,}\textkai{赖文昕}%
	\texstringonly{
		\textit{\small in collaboration with} \\
			Luis Apolo,
			Peng-Xiang Hao \textkai{郝鹏翔}
			and Wei Song \textkai{宋伟}\\[2ex]
		\sidenote{\arxiv{2303.04836}}%
%		\ submitted to \textit{JHEP}
	}%
}
\institute{\small%
	Yau Mathematical Sciences Center,\\
	Tsinghua\texstringonly{
%		\\\large\ccbyncsajp
	}\\[2ex]
	\today\ @ BIMSA
}
\date{}

@@

\begin{document}
{%%% TITLEPAGE
\setbeamercolor{title in head/foot}{
		use=palette quaternary
		,fg=palette quaternary.bg
	}
\logo{}
\begin{frame}
%	\titlegraphic{\vspace{2\baselineskip}}
	\titlepage
	\tikz [remember picture,overlay]
	\node at ([
		yshift=-4.6\baselineskip,
		xshift=.25\linewidth
	] current page.center) {
		\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[height=.33\textheight]{img/smbc-cantor-cropped.png}
		\\[.2ex]
		\footnotesize \url{https://smbc-comics.com/comic/cantor}
		\hspace{-1.5em}
		\end{minipage}
	};
\end{frame}
}%%% TITLEPAGE

\begin{frame}{Outline}
\raggedbottom
\large
\tableofcontents
\end{frame}

@@

\newcommand{\citeMaldacena}{%
	\textcite{Maldacena:1997re} --- \scriptsize\citetitle{Maldacena:1997re}
}

@@

\begin{frame}{AdS/CFT --- holography duality}{%
	\citeMaldacena%
}
\vspace{-2.5\baselineskip}
\stateAdsCft
\vspace{-1.8\baselineskip}
\begin{figure}[!h]
	\centering
	\includegraphics[width=.5\linewidth]{img/ads-cft.png}

	\vspace{-.3\baselineskip}
	\caption{$\mrm{AdS}_3/\mrm{CFT}_2$ cartoon}

	\vspace*{-.8\baselineskip}
	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
\end{figure}
\vspace{-1.3\baselineskip}
\end{frame}

@@

\begin{frame}{AdS/CFT --- a model of quantum gravity}{%
	\citeMaldacena
}
\vspace{-2.4\baselineskip}
\stateAdsCft
\vspace{-1.6\baselineskip}
\pause
\begin{itemize}

@@

\pause
\begin{itemize}
	\item Model agnostic: $\mrm{AdS}_5\times S^5$, $\mrm{AdS}_3\times S^3 \times T^4$, symmetric orbifolds, minimal models, ``monsters'', ... \textit{\small Maldacena, Witten, GKP, ABJM, Gaberdiel, and many many more}
	\item Our work: pure Einstein gravity in $\mrm{AdS}_3$ / $\mrm{CFT}_2$ $(d=2)$.

\end{itemize}
\end{itemize}
\end{frame}

%%% LaTeX3e!
\NewDocumentCommand{\figAdsCft}{ O{.28} }{
\begin{column}{#1\textwidth}
\begin{figure}[!h]
	\centering
	\includegraphics[width=\linewidth]{img/ads-cft-cleaner.png}

	\vspace{-.01\baselineskip}
	\scriptsize\textcite{AldegundePWSep22}\ \,
\end{figure}
\end{column}
}

\begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- gravity trapped in a cylinder}{%
	\textcite{Aharony:1999ti}
}
\begin{columns}
\figAdsCft
\begin{column}{.75\textwidth}
	\begin{itemize}
	\item $\mrm{AdS}_3$ metric, $\rho \sim z^2 \sim r^{-2}$
	\begin{equation}
	\hspace{-2em}
		ds^2 = \ell^2 \frac{d\rho^2}{4 \rho^2} + \pqty{\frac{1}{\rho} g^{(0)}_{ij} + g^{(2)}_{ij} + \rho\thinmspace g^{(4)}_{ij} + \cdots}\, dx^i dx^j \label{fggauge}
	\end{equation}

@@

\newcommand{\figCutoffAds}[1][.3]{
\begin{column}{#1\textwidth}
\begin{figure}[!h]
	\hfill\includegraphics[width=\linewidth]{img/cutoff-ads.jpg}

	\vspace{-.5\baselineskip}
	\flushleft
	\ \scriptsize\textcite{AldegundePWSep22}
\end{figure}
\end{column}
\hspace{-2em}
}

@@

\begin{frame}{Cutoff $\mrm{AdS}_3$ --- gravity in a box}{%
	Title inspired by
	\textcite{Kraus:2021cwf} -- \citetitle{Kraus:2021cwf}%
}
\begin{columns}
\figCutoffAds
\hspace{-1.2em}
\begin{column}{.75\textwidth}
\vspace{-.5\baselineskip}
	\begin{itemize}
	\item \textbf{Significance:} gravity inside a finite box\\
		with hard Dirichlet walls

@@

\newcommand{\figGlueon}[1][.37]{
\begin{column}{#1\textwidth}
\begin{figure}[!h]
	\centering
	\includegraphics[width=\linewidth]{img/diagram.pdf}
	\vspace{-1.5\baselineskip}
	\caption{Glue-on $\mrm{AdS}_3$}

	\vspace{-.3\baselineskip}
	\scriptsize\ Top-down view of the Poincar\'e disk
\end{figure}
\end{column}
}

\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar --- updating the dictionary}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}
\begin{columns}
\figGlueon
\begin{column}{.64\textwidth}
\vspace{-\baselineskip}
\begin{equation}
	\frac{1}{\zeta} \equiv \ell^{-2} g_{\varphi\varphi} \in \mbb{R},
\ \quad
	\zeta_c = - \frac{c \mu}{3\ell^2} \in \mbb{R}
\end{equation}
\vspace{-.5\baselineskip}
\begin{itemize}
\item What have we done other than copy-pasting?
	\begin{itemize}
	\item Although the continuation is straightforward, physical quantities diverge as $\rho \to 0$

@@

\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar --- the proposal}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}
\centering
\vspace{-.5\baselineskip}
\begin{minipage}{.5\textwidth}
\centering
\includegraphics[width=.9\linewidth]{img/diagram.pdf}
\end{minipage}
\vspace{-.1\baselineskip}
\begin{equation*}
\stateGlueon
\end{equation*}
\end{frame}

@@

\begin{frame}{\TTbar quantities from bulk geometry}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}
\begin{columns}
\figGlueon[.3]
\begin{column}{.75\textwidth}
\begin{itemize}
\item AdS/CFT: weak / strong duality
	\begin{itemize}
	\item \textit{quantum} quantities on the CFT side\\
		can be computed by (semi-)classical geometry
	\item inherited by the \TTbar deformation
	\end{itemize}

@@

\begin{frame}{\TTbar spectrum from bulk covariant charges}{%
	\textcite{Kraus:2021cwf,Apolo:2023vnm}
}
\begin{columns}
\figGlueon[.3]
\begin{column}{.75\textwidth}
\vspace{-.3\baselineskip}
\begin{itemize}
\item Spectrum: conserved charges of geometries,\\
	e.g.~black holes \textit{BTZ} \cite{Banados:1992wn}
	\begin{itemize}
	\item computed with the covariant formalism\\
		\textcite{Iyer:1994ys, Barnich:2001jy}
	\item manifest covariance (diff-invariance) depends on reparametrization redundancies (gauge),\\
		so delay gauge fixing until the very end
	\end{itemize}

@@

\begin{frame}{\TTbar partition functions from bulk on-shell actions}{%
	\textcite{Caputa:2020lpa}
}
\begin{columns}
\figGlueon
\hspace{-1.5em}
\begin{column}{.7\textwidth}
\vspace{-.3\baselineskip}
\begin{itemize}
\item Bulk: weakly coupled gravity, the partition function is approximated by the on-shell gravity action of the dominant saddle:
	\begin{equation}
		Z_{T\bar T} (\mu) = \mathcal Z (\zeta_c) \approx  e^{-I(\zeta_c)}\label{partition2}
	\end{equation}

@@

\begin{frame}{Comparison with field theory analysis}{%
	\textcite{Datta:2018thy,Apolo:2023aho}
}
\begin{columns}
%\figGlueon
%\hspace{-1.5em}
\begin{column}{\textwidth}
\vspace{-.3\baselineskip}
\begin{itemize}
\item \textbf{Torus:} Large $c$, \textit{modular invariance} \& sparseness of the ``light'' spectrum \cite{Datta:2018thy,Apolo:2023aho},
	c.f. \textcite{Hartman:2014oaa}
	\begin{equation*}
	\hspace{-1.5em}
		\log   Z_{T\bar T}(\mu)  \approx \left\{ \begin{aligned}
		& {-\frac{1}{2}}\,(\beta_L + \beta_R)\, RE_{\text{vac}}(\mu),  &\beta_L \beta_R > 1, \\
		& {-2 \pi^2 \bigg(\frac{1}{\beta_L} + \frac{1}{\beta_R}\bigg)  RE_{\text{vac}}\bigg(\frac{4\pi^2}{\beta_L \beta_R} \mu \bigg)}, \ \, &\beta_L\beta_R < 1, %\\[2ex]
		 \end{aligned} \right. %\label{ZTTbar}
	\end{equation*}

\item \textbf{Sphere:} maximally symmetric, \textcite{Donnelly:2018bef}
	\begin{equation}
%		\label{sphere:stresstensor}
		\langle T_{ij}\rangle =-\frac{1}{4\pi\mu} \bigg(1-\sqrt{1-\frac{c\mu}{3L^2}}\, \bigg)  \gamma_{ij}.
	\end{equation}
\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Sphere partition functions}{%
	\textcite{Donnelly:2018bef,Li:2020zjb}
}
\begin{columns}
%\figGlueon
%\hspace{-1.5em}
\begin{column}{\textwidth}
\vspace{-.3\baselineskip}
\begin{itemize}

@@

	\item \textcite{Donnelly:2018bef} is recovered with $a = \sqrt{c|\mu|/3}$ but one can also take $a = \epsilon$, thus decoupling the energy (RG) scale $\epsilon$ with the deformation $\mu$. 
\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Gravitational actions: with counterterms}{%
	\textcite{Donnelly:2018bef,Li:2020zjb}
}
\begin{columns}
%\figGlueon
%\hspace{-1.5em}
\begin{column}{1.1\textwidth}
\vspace{-.3\baselineskip}
\begin{itemize}

@@

\begin{frame}{Gravitational actions: with counterterms}{%
	\textcite{Caputa:2020lpa,Li:2020zjb}
}
\begin{columns}
%\figGlueon
%\hspace{-1.5em}
\begin{column}{1.1\textwidth}
\vspace{-.3\baselineskip}
\begin{itemize}

@@

\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar deformed $\mrm{CFT}_2$}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}
\vspace{-2\baselineskip}
\begin{equation*}
\stateGlueon
\end{equation*}
\vspace{-1.3\baselineskip}
\begin{columns}
\begin{column}{.37\textwidth}
\begin{figure}[!h]
	\centering
	\includegraphics[width=\linewidth]{img/RT-AdS.pdf}
	\vspace{-1.5\baselineskip}
	\caption{RT for Glue-on $\mrm{AdS}_3$}

	\vspace{-.3\baselineskip}
	\scriptsize\, Top-down view of the Poincar\'e disk
\end{figure}
\end{column}
\hspace{-1em}
\begin{column}{.71\textwidth}
\begin{itemize}
\item Holographic proposal for $T\bar T$-deformed CFTs\\
with $\mu \in \mbb{R}$.

@@

\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar deformed $\mrm{CFT}_2$}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}
\vspace{-2\baselineskip}
\begin{equation*}
\stateGlueon
\end{equation*}
\vspace{-1.3\baselineskip}
\begin{columns}
\begin{column}{.37\textwidth}
\begin{figure}[!h]
	\centering
	\includegraphics[width=\linewidth]{img/RT-AdS.pdf}
	\vspace{-1.5\baselineskip}
	\caption{RT for Glue-on $\mrm{AdS}_3$}

	\vspace{-.3\baselineskip}
	\scriptsize\, Top-down view of the Poincar\'e disk
\end{figure}
\end{column}
\hspace{-1em}
\begin{column}{.71\textwidth}
\begin{itemize}

@@

\begin{frame}

@@

\begin{frame}[allowframebreaks]{References}
\renewcommand*{\bibfont}{\footnotesize}
\printbibliography %%% should not specify heading etc
\end{frame}

>>>>

\documentclass[10pt]{article}

\input{preamble-slides.tex}

\usepackage{tikz}
\usepackage{caption}
%\usepackage{snapshot}

\renewenvironment{frame}[1]%
	{\section*{#1}}%
	{\clearpage}

\newcommand{\pause}{}

\newenvironment{columns}%
	{\par\begin{minipage}{\textwidth}}%
	{\end{minipage}}

\newenvironment{column}[1]%
	{\begin{minipage}{#1}}%
	{\end{minipage}}

\title{Glue-on AdS holography for $T\bar T$-deformed CFTs}
%\subtitle{An extended AdS\,/\,\TTbar duality \textit{(beyond infinity)}}
\author{%
	Wen-Xin Lai
	\texstringonly{\,}\textkai{赖文昕}%
}
\date{}

@@

\begin{document}

\setlength{\droptitle}{-3.5\baselineskip}
\maketitle
\thispagestyle{empty}

\vspace{-3.5\baselineskip}

\textit{in collaboration with}
\\[.8ex]
	{\large Luis Apolo,
	Peng-Xiang Hao \textkai{郝鹏翔}
	and Wei Song \textkai{宋伟}}
\\[2ex]
	\sidenote{\arxiv{2303.04836}}
\\[3ex]
	\textsf{Yau Mathematical Sciences Center, Tsinghua}
\\[1ex]
	{\large\ccbyncsajp}
\\[2ex]
	\textsf{\today\ @ BIMSA}
\\[4ex]
	\includegraphics[height=.38\textheight]{img/smbc-cantor-cropped.png}
\\[-.5ex]
	{\footnotesize\url{https://smbc-comics.com/comic/cantor}}

\clearpage
\justifying

%\raggedbottom
\large
\tableofcontents
\pagebreak

@@

\newcommand{\citeMaldacena}{%
	\textcite{Maldacena:1997re}
}

@@

\citeMaldacena
\stateAdsCft
\begin{figure}[!h]
	\centering
	\includegraphics[width=.5\linewidth]{img/ads-cft.png}

	\vspace{-.2\baselineskip}
	\caption{$\mrm{AdS}_3/\mrm{CFT}_2$ cartoon}

	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
\end{figure}
\vspace{-1.3\baselineskip}

@@

\section*{AdS/CFT --- a model of quantum gravity}
\citeMaldacena
\stateAdsCft
\begin{itemize}

@@

\begin{itemize}
	\item Model agnostic: $\mrm{AdS}_5\times S^5$, $\mrm{AdS}_3\times S^3 \times T^4$, symmetric orbifolds, minimal models, ``monsters'', ... \textit{\small Maldacena, Witten, GKP, ABJM, Gaberdiel, and many many more}
	\item Our work: pure Einstein gravity in $\mrm{AdS}_3$ / $\mrm{CFT}_2$ $(d=2)$.

\end{itemize}
\end{itemize}

\pagebreak

%%% LaTeX3e!
\NewDocumentCommand{\figAdsCft}{ O{.28} }{
\begin{minipage}{#1\textwidth}
	\centering
	\includegraphics[width=\linewidth]{img/ads-cft-cleaner.png}

	\vspace{-.01\baselineskip}
	\scriptsize\textcite{AldegundePWSep22}\ \,
\end{minipage}
}

\begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- gravity trapped in a cylinder}

\textcite{Aharony:1999ti}

\begin{columns}
\figAdsCft
\begin{column}{.72\textwidth}
	\begin{itemize}
	\item $\mrm{AdS}_3$ metric, $\rho \sim z^2 \sim r^{-2}$
	\begin{equation}
	\hspace{-2em}
		ds^2 = \ell^2 \frac{d\rho^2}{4 \rho^2} + \pqty{\frac{1}{\rho} g^{(0)}_{ij} + g^{(2)}_{ij} + \rho\thinmspace g^{(4)}_{ij} + \cdots}\, dx^i dx^j \label{fggauge}
	\end{equation}

@@

\newcommand{\figCutoffAds}[1][.3]{
\begin{column}{#1\textwidth}
	\hfill\includegraphics[width=\linewidth]{img/cutoff-ads.jpg}

	\vspace{-.5\baselineskip}
	\flushleft
	\ \scriptsize\textcite{AldegundePWSep22}
\end{column}
\hspace{-2em}
}

@@

\begin{frame}{Cutoff $\mrm{AdS}_3$ --- gravity in a box}{%
	Title inspired by
	\textcite{Kraus:2021cwf} -- \citetitle{Kraus:2021cwf}%
}
\begin{columns}
\figCutoffAds
\hspace{-1.2em}
\begin{column}{.72\textwidth}
\vspace{-.5\baselineskip}
	\begin{itemize}
	\item \textbf{Significance:} gravity inside a finite box\\
		with hard Dirichlet walls

@@

\newcommand{\figGlueon}[1][.37]{
\begin{minipage}{#1\textwidth}
	\centering
	\includegraphics[width=\linewidth]{img/diagram.pdf}
	\vspace{-1.5\baselineskip}
	\captionsetup{type=figure}
	\caption{Glue-on $\mrm{AdS}_3$}

	\vspace{-.3\baselineskip}
	\scriptsize\ Top-down view of the Poincar\'e disk
\end{minipage}
}

\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar --- updating the dictionary}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}
\begin{columns}
\figGlueon
\begin{column}{.6\textwidth}
\begin{equation}
	\frac{1}{\zeta} \equiv \ell^{-2} g_{\varphi\varphi} \in \mbb{R},
\ \quad
	\zeta_c = - \frac{c \mu}{3\ell^2} \in \mbb{R}
\end{equation}
\begin{itemize}
\item What have we done other than copy-pasting?
	\begin{itemize}
	\item Although the continuation is straightforward, physical quantities diverge as $\rho \to 0$

@@

\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar --- the proposal}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}

\begin{minipage}{.5\textwidth}
\centering
\includegraphics[width=.9\linewidth]{img/diagram.pdf}
\end{minipage}

\begin{equation*}
\stateGlueon
\end{equation*}
\end{frame}

@@

\begin{frame}{\TTbar quantities from bulk geometry}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}
\begin{columns}
\figGlueon[.3]
\begin{column}{.7\textwidth}
\begin{itemize}
\item AdS/CFT: weak / strong duality
	\begin{itemize}
	\item \textit{quantum} quantities on the CFT side\\
		can be computed by (semi-)classical geometry
	\item inherited by the \TTbar deformation
	\end{itemize}

@@

\begin{frame}{\TTbar spectrum from bulk covariant charges}{%
	\textcite{Kraus:2021cwf,Apolo:2023vnm}
}
\begin{columns}
\figGlueon[.3]
\begin{column}{.7\textwidth}
\begin{itemize}
\item Spectrum: conserved charges of geometries,\\
	e.g.~black holes \textit{BTZ} \cite{Banados:1992wn}
	\begin{itemize}
	\item computed with the covariant formalism\\
		\textcite{Iyer:1994ys, Barnich:2001jy}
	\item manifest covariance (diff-invariance) depends on reparametrization redundancies (gauge),\\
		so delay gauge fixing until the very end
	\end{itemize}

@@

\begin{frame}{\TTbar partition functions from bulk on-shell actions}{%
	\textcite{Caputa:2020lpa}
}
\begin{columns}
\figGlueon
\hspace{-1.5em}
\begin{column}{.6\textwidth}
\vspace{-.3\baselineskip}
\begin{itemize}
\item Bulk: weakly coupled gravity, the partition function is approximated by the on-shell gravity action of the dominant saddle:
	\begin{equation}
		Z_{T\bar T} (\mu) = \mathcal Z (\zeta_c) \approx  e^{-I(\zeta_c)}\label{partition2}
	\end{equation}

@@

\begin{frame}{Comparison with field theory analysis}{%
	\textcite{Datta:2018thy,Apolo:2023aho}
}

\vspace{-.3\baselineskip}

\begin{itemize}
\item \textbf{Torus:} Large $c$, \textit{modular invariance} \& sparseness of the ``light'' spectrum \cite{Datta:2018thy,Apolo:2023aho},
	c.f. \textcite{Hartman:2014oaa}
	\begin{equation*}
	\hspace{-1.5em}
		\log   Z_{T\bar T}(\mu)  \approx \left\{ \begin{aligned}
		& {-\frac{1}{2}}\,(\beta_L + \beta_R)\, RE_{\text{vac}}(\mu),  &\beta_L \beta_R > 1, \\
		& {-2 \pi^2 \bigg(\frac{1}{\beta_L} + \frac{1}{\beta_R}\bigg)  RE_{\text{vac}}\bigg(\frac{4\pi^2}{\beta_L \beta_R} \mu \bigg)}, \ \, &\beta_L\beta_R < 1, %\\[2ex]
		 \end{aligned} \right. %\label{ZTTbar}
	\end{equation*}

\item \textbf{Sphere:} maximally symmetric, \textcite{Donnelly:2018bef}
	\begin{equation}
%		\label{sphere:stresstensor}
		\langle T_{ij}\rangle =-\frac{1}{4\pi\mu} \bigg(1-\sqrt{1-\frac{c\mu}{3L^2}}\, \bigg)  \gamma_{ij}.
	\end{equation}
\end{itemize}
\end{frame}

\begin{frame}{Sphere partition functions}{%
	\textcite{Donnelly:2018bef,Li:2020zjb}
}

\begin{itemize}

@@

	\item \textcite{Donnelly:2018bef} is recovered with $a = \sqrt{c|\mu|/3}$ but one can also take $a = \epsilon$, thus decoupling the energy (RG) scale $\epsilon$ with the deformation $\mu$. 
\end{itemize}
\end{frame}

\begin{frame}{Gravitational actions: with counterterms}{%
	\textcite{Donnelly:2018bef,Li:2020zjb}
}

\begin{itemize}

@@

\begin{frame}{Gravitational actions: with counterterms}{%
	\textcite{Caputa:2020lpa,Li:2020zjb}
}

\begin{itemize}

@@

\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar deformed $\mrm{CFT}_2$}
\noindent
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}

\begin{equation*}
\stateGlueon
\end{equation*}

\begin{columns}
\begin{column}{.37\textwidth}
	\centering
	\includegraphics[width=\linewidth]{img/RT-AdS.pdf}
	\vspace{-1.5\baselineskip}
	\captionof{figure}{RT for Glue-on $\mrm{AdS}_3$}

	\vspace{-.3\baselineskip}
	\scriptsize\, Top-down view of the Poincar\'e disk
\end{column}
\hspace{-1em}
\begin{column}{.65\textwidth}
\begin{itemize}
\item Holographic proposal for $T\bar T$-deformed CFTs\\
with $\mu \in \mbb{R}$.

@@

\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar deformed $\mrm{CFT}_2$}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}
\begin{equation*}
\stateGlueon
\end{equation*}
\begin{columns}
\begin{column}{.3\textwidth}
	\centering
	\includegraphics[width=\linewidth]{img/RT-AdS.pdf}
	\vspace{-1.5\baselineskip}
	\captionof{figure}{RT for Glue-on $\mrm{AdS}_3$}

	\vspace{-.3\baselineskip}
	\scriptsize\, Top-down view of the Poincar\'e disk
\end{column}
\hspace{-1em}
\begin{column}{.71\textwidth}
\begin{itemize}

@@

\begin{frame}{}

@@

\begin{frame}{}
\renewcommand*{\bibfont}{\footnotesize}
\printbibliography %%% should not specify heading etc
\end{frame}
